---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `uwu` (ꈍᴗꈍ)♡

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of uwu like so:

This requires Rust to be installed. 

``` r
if (requireNamespace("pak")) install.packages("pak")
pak::pak("josiahparry/uwu")
```



## Example

Generate v4 UUIDs ~20x faster than `uuid` 

```{r example}
library(uwu)
new_v4(10)
```

Or you can generate v7 UUIDs ~2.5x slower than `uuid` 

```{r}
new_v7(10)
```

The neat part, though, is that we can impute a UUID into a character vector by reference. This means that once the operation has occured, you cannot take it back!!

```{r}
x <- c("a", NA, "c")

# x has been imputed 
impute_uuid(x)

x
```

It can also have a prefix added to it:

```{r}
x <- c("a", NA, "c")

# x has been imputed 
impute_uuid(x, prefix = "NA_")
x
```

Here's an example to address the problem that prompted this.

```{r}
# define a data.frame with missing values 
to_impute <- data.frame(
  col_a = c("one", "two", NA),
  col_b = c("a", NA, "c"),
  col_c = c(NA, "and", "me")
)

df_names <- colnames(to_impute)

for (j in seq_along(to_impute)) {
    impute_uuid(to_impute[[j]], paste0("NA_", df_names[j], "_"))
}

to_impute
```

### Short uuids:

Generate short uuid string (default flickrBase58 alphabet)

```{r}
n <- 10
new_short(n)
```


Bitcoin58 example:

```{r}
new_short(n, "bitcoin58")
```

Convert uuid V4 to short (default flickrBase58 alphabet)


```{r}
uuids <- new_v4(n)
uuids
```

```{r}
su_flickr <- uuid_to_short(uuids)
su_flickr
```


```{r}
su_bitcoin <- uuid_to_short(uuids, "bitcoin58")
su_bitcoin
```


Convert short uuid to uuid (default flickrBase58 alphabet)
```{r}
uuids2 <- short_to_uuid(su_flickr)
uuids2
```

```{r}
uuids3 <- short_to_uuid(su_bitcoin, "bitcoin58")
uuids3
```

comparison

```{r}
identical(uuids, uuids2)
identical(uuids, uuids3)
```
